Museum specimens as baseline for assessing a potential global pollinator crisis

### 2018-02-05 ms.Rmd
Try logs on Fig 2

plot(lhf$percent_post1980, lhf$percent_pre1980, xlab = "post1980", ylab = "pre1980", col = as.factor(lhf$country), xlim = c(0,1), ylim = c(0, 1))
abline(h = 0.50, v = 0.50)
```
This is even worst... correcting for size would be the best BUT I don't think richness and size have a linear relationship, so we should account for that then??

>>>>

plot(lhf$percent_post1980, lhf$percent_pre1980, xlab = "post1980", ylab = "pre1980", col = as.factor(lhf$country), xlim = c(0,1), ylim = c(0, 1))
abline(h = 0.50, v = 0.50)

plot(log(lhf$post1980+1), log(lhf$pre1980+1), xlab = "post1980", ylab = "pre1980", col = as.factor(lhf$country))
abline(h = 8, v = 8)

```
This is even worst... correcting for size would be the best BUT I don't think richness and size have a linear relationship, so we should account for that then??
Simply logging the data may work, we can point out % of countries with > 1000 records in either axes, for example, etc...
